A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-16 mt-marathon.2013/PBML_article.tex
changes

\section{File Format}
\subsection{Old Framework}
Each feature function also required a separate section in the configuration (moses.ini) file to be created, along with the code to read the new section. For example, translation models are specified in the section
\begin{verbatim}
     [ttable-file]
\end{verbatim}
Language models are in
\begin{verbatim}
     [lmodel-file]
\end{verbatim}
Similarly, each feature function also need a separate weight section, for example, for translation models:
\begin{verbatim}
     [weight-t]
\end{verbatim}
and language models:
\begin{verbatim}
     [weight-l]
\end{verbatim}
New feature functions need to create and manage their own specification and weight sections.

The tuning script must also be informed of new weight sections by manually editing the MERT script.

\subsection{New Framework}
The configuration file format has been changed to minimize the amount of code changes necessary when adding new feature functions. All feature functions are declared in the configuration file in the section
\begin{verbatim}
  [feature]
\end{verbatim}
In the fixed format
\begin{verbatim}
  Feature-Name [key=value]*
\end{verbatim}
Similarly, all dense \emph{weights} are put into the section
\begin{verbatim}
  [weight]
\end{verbatim}
In the fixed format
\begin{verbatim}
  Feature-Instance= [value]*
\end{verbatim}
Weights for sparse features are in separate file referenced by the section
\begin{verbatim}
  [weight-file]
\end{verbatim}
in the format
\begin{verbatim}
  Feature-Instance feature value
\end{verbatim}
The following is an example section from a vanilla phrase-based configuration file:
\begin{verbatim}
  [feature]
  UnknownWordPenalty
  WordPenalty
  PhraseDictionaryMemory name=TranslationModel0 table-limit=20 num-features=5...
  LexicalReordering name=LexicalReordering0 num-features=6 type=wbe-msd...
  Distortion
  KENLM lazyken=1 name=LM0 factor=0 path=europarl.binlm.1 order=5
\end{verbatim}
Notice that feature functions \emph{UnknownWordPenalty}, \emph{WordPenalty}, and \emph{Distortion} must be explicitly specified. In the old format, these features were implicitly included for all phrase-based models.

The weights section from the same moses.ini file is shown below:
\begin{verbatim}
  [weight]
  UnknownWordPenalty0= 1
  WordPenalty0= -1
  TranslationModel0= 0.2 0.2 0.2 0.2 0.2
  LexicalReordering0= 0.3 0.3 0.3 0.3 0.3 0.3
  Distortion0= 0.3
  LM0= 0.5
\end{verbatim}

>>>>

% \section{File Format}
% \subsection{Old Framework}
% Each feature function also required a separate section in the configuration (moses.ini) file to be created, along with the code to read the new section. For example, translation models are specified in the section
% \begin{verbatim}
%      [ttable-file]
% \end{verbatim}
% Language models are in
% \begin{verbatim}
%      [lmodel-file]
% \end{verbatim}
% Similarly, each feature function also need a separate weight section, for example, for translation models:
% \begin{verbatim}
%      [weight-t]
% \end{verbatim}
% and language models:
% \begin{verbatim}
%      [weight-l]
% \end{verbatim}
% New feature functions need to create and manage their own specification and weight sections.
% 
% The tuning script must also be informed of new weight sections by manually editing the MERT script.
% 
% \subsection{New Framework}
% The configuration file format has been changed to minimize the amount of code changes necessary when adding new feature functions. All feature functions are declared in the configuration file in the section
% \begin{verbatim}
%   [feature]
% \end{verbatim}
% In the fixed format
% \begin{verbatim}
%   Feature-Name [key=value]*
% \end{verbatim}
% Similarly, all dense \emph{weights} are put into the section
% \begin{verbatim}
%   [weight]
% \end{verbatim}
% In the fixed format
% \begin{verbatim}
%   Feature-Instance= [value]*
% \end{verbatim}
% Weights for sparse features are in separate file referenced by the section
% \begin{verbatim}
%   [weight-file]
% \end{verbatim}
% in the format
% \begin{verbatim}
%   Feature-Instance feature value
% \end{verbatim}
% The following is an example section from a vanilla phrase-based configuration file:
% \begin{verbatim}
%   [feature]
%   UnknownWordPenalty
%   WordPenalty
%   PhraseDictionaryMemory name=TranslationModel0 table-limit=20 num-features=5...
%   LexicalReordering name=LexicalReordering0 num-features=6 type=wbe-msd...
%   Distortion
%   KENLM lazyken=1 name=LM0 factor=0 path=europarl.binlm.1 order=5
% \end{verbatim}
% Notice that feature functions \emph{UnknownWordPenalty}, \emph{WordPenalty}, and \emph{Distortion} must be explicitly specified. In the old format, these features were implicitly included for all phrase-based models.
% 
% The weights section from the same moses.ini file is shown below:
% \begin{verbatim}
%   [weight]
%   UnknownWordPenalty0= 1
%   WordPenalty0= -1
%   TranslationModel0= 0.2 0.2 0.2 0.2 0.2
%   LexicalReordering0= 0.3 0.3 0.3 0.3 0.3 0.3
%   Distortion0= 0.3
%   LM0= 0.5
% \end{verbatim}
